---
title: Data Contributor Materials
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(downloadthis)
```

## Data Curation Materials

Data and metadata template downloads

```{r}

## Download one file
download_file(
  path = "downloads/templates/ccrcn_cores_template.xlsx",
  output_name = "ccrcn_cores_template", # left off here
  output_extension = ".xlsx",
  button_label = "Download Core Template",
  button_type = "info",
  has_icon = TRUE,
  icon = "fa fa-save",
  self_contained = FALSE
)

# other examples
# https://fmmattioni.github.io/downloadthis/articles/downloadthis.html
```

```{r}
# download zip file
  download_dir(
    path = "downloads/templates",
    output_name = "ccrcn_data_templates",
    button_label = "Download all templates",
    button_type = "primary",
    has_icon = TRUE,
    icon = "fa fa-save"
  )
```

## References

Standards and Catalogs:

- [ISO Geodetic Registry](https://geodetic.isotc211.org/register/geodetic/VerticalDatum)
- [NOAA Tidal Datums](https://tidesandcurrents.noaa.gov/datum_options.html)
- Controlled vocabulary for keywords?
- EML standard units

## Publications for Thought

Wilson, G., Bryan, J., Cranston, K., Kitzes, J., Nederbragt, L., & Teal, T. K. (2017). Good enough practices in scientific computing. PLoS computational biology, 13(6), e1005510. https://doi.org/10.1371/journal.pcbi.1005510

Serwadda, D., Ndebele, P., Grabowski, M. K., Bajunirwe, F., & Wanyenze, R. K. (2018). Open data sharing and the Global South—Who benefits?. Science, 359(6376), 642-643. https://doi.org/10.1126/science.aap8395

